Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-26 paper.tex
Added awesome graph

@@

The continuous benchmark has more surprising results. Notice that Figure
\ref{fig:swap_time_cont} has a logarithmic y-scale. The system only begins to
swap after about 4M operations, as before. Unlike the random benchmark, we see a
number of operations that take hundreds of milliseconds. Figure
\ref{fig:swap_time_cont_cdf} shows that these only form a fraction of a percent
of all accesses done after swapping starts. However, Figure (TODO: figure) shows
that these few accesses form a majority of run time; they impact performance
significantly. (TODO: why do they happen).

We also find that in the continuous benchmark, a larger swapfile actually has
slight more of these slow memory accesses. We believe this has to do with the
fact that the large swapfile has less disk locality, and so causes more disk
seeks when paging out.

~\\ \textbf{Conclusions} TODO

@@

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cdf}
    \caption{CDF of amount of time spent on operations with a given
    latency.\label{fig:swap_time_cdf}}
\end{figure}

@@

The continuous benchmark has more surprising results. Notice that Figure
\ref{fig:swap_time_cont} has a logarithmic y-scale. The system only begins to
swap after about 4M operations, as before. Unlike the random benchmark, we see a
number of operations that take hundreds of milliseconds. Figure
\ref{fig:swap_time_cont_cdf} shows that these only form a fraction of a percent
of all accesses done after swapping starts. However, Figure
\ref{fig:swap_time_cdf} shows that these few accesses form a majority of run
time; they impact performance significantly. (TODO: why do they happen?).

We also find that in the continuous benchmark, a larger swapfile actually has
slight more of these slow memory accesses. We believe this has to do with the
fact that the large swapfile has less disk locality, and so causes more disk
seeks when paging out. Figure \ref{fig:swap_time_cdf} shows that with a larger
swapfile, the continuous benchmark has a significantly higher number of
high-latency accesses as compared with the smaller swapfile.

~\\ \textbf{Conclusions}

@@

Looking at 99.99-th percentile latencies is important because they can have a
lot of impact on overall run time.

TODO: what else?
